Autogenerated Questions Paper Draft

### 2018-03-22 paper_draft/paper_draft.tex
Finish all categories and add some notes for revision/further sections

@@

@@

@@

@@

The main objective here is to test students on reference parameters . This is possible to test with only one variable, but that limits the difficulty (as well as the overall randomness) that is the goal of these questions. Conversely, some may argue that three parameters is too complex in itself. In the current implementation, the number of variables (as well as the number of parameters) are constant, but can be easily changed and easily randomized if desired. Another option for added randomization is the datatype of all parameters and all variables (currently, only integers are used). A couple final static elements of this question are a) the order that the

Despite all of these static elements, there are still many options for randomization

@@

%TODO

@@

%TODO

>>>>

%\usepackage{listings}
%\usepackage{fancyvrb}
%\usepackage{verbatim}

@@

NOTE: maybe here is the place to quickly differentiate between 1) the program code, 2) the GIFT code it generates (which is shown below), and 3) the code the students are learning (mostly seen in each category with the examples).

@@

\subsection{Convincing Distractors}

NOTE: Before we talk about unique answer guarantee, we should talk about distractors: what they are, why they are important, how others use them/disregard them/why they should be convincing. Also we should provide some concrete examples.

@@

\subsection{Prevention of Trivial Cases}

NOTE: Maybe here is a quick section where we talk about preventing trivial cases. Each category looks for cases like (x - x), and x / 1, etc. Also should we talk about trivial distractors -- similar to how the unique answer guarantee basically falls on trivial answers as a last resort.

@@

The main objective here is to test students on reference parameters . This is possible to test with only one variable, but that limits the difficulty (as well as the overall randomness) that is the goal of these questions. Conversely, some may argue that three parameters is too complex in itself. In the current implementation, the number of variables (as well as the number of parameters) are constant, but can be easily changed and easily randomized if desired. Another option for added randomization is the datatype of all parameters and all variables (currently, only integers are used). The final static elements of this question are a) the order that the variables are defined in is the same order that the variables are passed to the function; b) the variable printed at the end of the prompt always corresponds to the parameter that is assigned in the function; c) the order that the parameters are defined in is the same order they appear in the expression; and d) the number of operands in the expression is the same as the number of parameters. All of these elements can be randomized, but again, they usually add difficulty without changing the essence of the question.

Despite all of these static elements, there are still many options for randomization.  Most importantly, each parameter has a 50/50 chance of being pass-by-reference or pass-by-value and the parameter that is assigned in the function. In addition, the regular randomization methods for creating expressions (with random operators) and assigning operand values are used.

Because this question depends on the expression inside the function, some of the same distractor methods are used within this category, such as disregarding order of operations and
using float values and float operations. The novel distractor methods are much more interesting.
The first (and most obvious method) distractor being equal to the original value of the variable -- if the parameter is pss-by-reference -- or the value of the expression -- if the parameter is pass-by-value. A fairly straightforward method, but effective in testing the objective of this question. 
The next distractor is simply the value of the variable declared after the printed variable (in the example above, this would be item). This method is not as particularly sophisticated, but serves as an obvious wrong answer for knowledgeable students.

@@

- Actual testing (statistics)

- More categories/better questions

- Better distractors

- Also maybe testing of distractor methods? Like how often does a distractor produce a non-unique answer? How often is a distractor actually convincing? This would need a group to review a set of questions.

- Better difficulty classification (also note that this is hard to do ethically)

@@

- A good framework for implementing, generating questions to be easily uploaded online.
